### 2018-07-18 experiments.tex
mutation experiment start

>>>>

\subsubsection{Mutation analysis}

We ran 2,350 mutants of pyfakefs.  Using the failure determinism check
in 60 second test runs let us kill 98 mutants that were not killed
during 60 seconds of testing without a reference or the failure
determinism check, using the same seed.  Of these, 71 could not even be killed by 120
seconds of testing using complete differential testing with Mac OS X
as a reference.  In contrast, the kill rate for the entire set of
mutants not killed without a reference, using 120 seconds of
differential testing was...
